\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{
		TARA AMBALE AWOII\\
		 16/U/11837/EVE \\
		 216018402
		}
\title{INDIVIDUAL RESEARCH}
\begin{document}
	\maketitle {\Large \begin{center}
		RESEARCH ON WHY DOGS ARE THE MOST PREFERRED PETS.
\end{center}}

\begin{flushleft}
	This research is carried out to find out why people prefer dogs as better pets compared to other animals. Dogs are considered as pets for many reasons and have been referred to as 'man's best friend'. This research gives the various reasons as to why dogs are the better pets.
	\linebreak
	\linebreak
	Research is also carried out to find out the benefits of having dogs as pets.
	\linebreak
	\linebreak
	Studies have shown that dogs are known to improve physical and mental health. There are many types of dogs and each dog can suit the lifestyle and and environment the owner lives in. This makes dogs better pets as they are easily adaptable.
	\linebreak
	\linebreak
	 The Huffington Post carried out a survey on the benefits and importance of having a dog as a pet. One of the most important benefits they cited was how having a dog could improve heart health of the owner and actually make their heart stronger. A canine companion is linked to lower blood pressure, reduced cholesterol and decreased triglyceride levels which in turn contribute to better overall cardiovascular health and fewer heart attacks. 
	 \linebreak
	 \linebreak
	 There are many other benefits to having a dog as a pet. These include the ability of dogs being able to detect life threatening diseases for example they can sniff out cancer, and epilepsy. There are other species of dogs that can be trained to act as guide dogs for visually impaired people and for physically impaired people.
	 \linebreak
	 \linebreak
	 \newpage 
	 In addition to being helpful medically, dogs are also wonderful guards and are used everywhere from the army to simple house guards. dogs have a strong sense of smell and can easily sense dangerous firearms to narcotic drugs.
\end{flushleft}
\end{document}